From physical principles to ???

### 2015-10-22 2015CompleteDerivation/completeDerivation.tex
Adding vector space definition and justification

labels/state variables, cardinality of state variable, state id function (=1 for a particular state). Can we do for continuous variables as well? Can we find divergence free evolution for det/rev and independent variables?

@@

If the scale of the problem

>>>>

TODO: labels/state variables, cardinality of state variable, state id function (=1 for a particular state). Can we do for continuous variables as well? Can we find divergence free evolution for det/rev and independent variables?

\section{Composite systems and reducibility}

We know introduce the idea that a system is decomposable, that is it is made of smaller parts, and we characterize the relationship between the whole and the parts with the following assumption:

@@

TODO:

\begin{defn}\label{vector space}
The state space $\mathfrak{C}$ for a infinitesimally reducible system is a vector space. Such vector is free, and admits a basis $\mathfrak{S}$ that represent the state space for the infinitesimal parts.
\end{defn}

\textbf{Justification}. We first claim that the state space $\mathfrak{C}$ is an additive monoid: there exist a law of composition $+ : \mathfrak{C} \times \mathfrak{C} \rightarrow \mathfrak{C}$ that takes two states and returns one that is the physical composition of the two. The domain and codomain match because the system is homogeneous. The law is commutative $\mathfrak{c}_1 +\mathfrak{c}_2 = \mathfrak{c}_2+\mathfrak{c}_1$ and associative $(\mathfrak{c}_1 + \mathfrak{c}_2) + \mathfrak{c}_3 = \mathfrak{c}_1 + (\mathfrak{c}_2 + \mathfrak{c}_3)$, as it does not matter in what order we compose the parts. There exist a zero element $\mathfrak{c} + 0 = \mathfrak{c}$ and it represent the state with no system.

We then claim it is an additive group. As we want to describe changes during the evolution, i.e. $\Delta \mathfrak{c}$, we introduce an inverse $\mathfrak{c}_2$ for each element $\mathfrak{c}_1$ such that $\mathfrak{c}_1 + \mathfrak{c}_2 = 0$. Such inverse may not represent a true physical state, yet we'll still call $\mathfrak{C}$ the state space committing an abuse of terminology. Having an inverse, $\mathfrak{C}$ is an additive (i.e. abelian) group.

We now consider the set of transformations $A$ that increase or decrease the size of the system by a constant. This forms a field\footnote{Here field is intended in the abstract algebraic sense (a nonzero commutative division ring) which has no relationship to the field in the physics sense (a physical quantity with a value for each point in space).} that is isomorphic to $\mathbbm{R}$. In fact, let $a: \mathbbm{R} \rightarrow A$ be a mapping between a number and the transformation that increases or decreases the size of the system by that number; define on $A$ an addition $+: A \times A \rightarrow A$ and a multiplication $*: A \times A \rightarrow A$ such that $a(x) + a(y) = a(x+y)$ and $a(x) * a(y) = a(x*y)$, so that the sum and product of the transformation is equal to the sum and product of their respective factors. $A$ is a field, as its sum and multiplication have all properties of $\mathbbm{R}$ which is a field. $a$ is an homomorphism by definition and is invertible by the very definition of $A$, each element fully identified by its constant. Therefore $A$ and $\mathbbm{R}$ are isomorphic.

We now claim that the state space $\mathfrak{C}$ is a vector space over $\mathbbm{R}$. The abelian group $\mathfrak{C}$ can be extended with the operations defined by $A$, as each element $a \in A$ is a map $a : \mathfrak{C} \rightarrow \mathfrak{C}$. The map has the following properties: $(a_1 + a_2) \mathfrak{c} = a_1 \mathfrak{c} + a_2 \mathfrak{c}$, increasing the size of the system by the sum of two constant is the same as combining the separate increases, and $a (\mathfrak{c}_1 + \mathfrak{c}_2) = a \mathfrak{c}_1 + a \mathfrak{c}_2$, increasing the size of the total system is the same as the combination of the increased parts. $\mathfrak{C}$ is a module over $A$, which is a field and isomorphic to $\mathbbm{R}$. We can then think of $\mathfrak{C}$ as a vector space over $\mathbbm{R}$.
